Paper Title

### 2023-09-01 paper.tex
Update PDF title
Explain better figure references

\documentclass[letterpaper,12pt,leqno]{article}
\usepackage{paper}
\bibliographystyle{bibliography}
% Enter paper title:
\hypersetup{pdftitle={Paper Example}}
% Enter permanent URL to paper
\available{https://github.com/pmichaillat/latex-paper}
% Enter BibTeX file with references:
\newcommand{\bib}{bibliography.bib}
% Enter PDF file with figures here:
\newcommand{\pdf}{figures.pdf}

@@

@@

\paragraph{Another paragraph} Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Figure~\ref{f:graph1} depicts the result.

\paragraph{Another result in a panel} Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Figure \ref{f:panel1} displays cum soluta nobis est eligendi optio, cumque nihil impedit. Quod maxime placeat, facere possimus, omnis voluptas assumenda est in figure \ref{f:panel2}.

\subsection{A full-page graphs}

>>>>

\documentclass[letterpaper,12pt,leqno]{article}
\usepackage{paper}
\bibliographystyle{bibliography}
% Enter paper title:
\hypersetup{pdftitle={Paper Title}}
% Enter permanent URL to paper
\available{https://github.com/pmichaillat/latex-paper}
% Enter BibTeX file with references:
\newcommand{\bib}{bibliography.bib}
% Enter PDF file with figures here:
\newcommand{\pdf}{figures.pdf}

@@

\paragraph{Paragraph with references to figures and panels} It is possible to refer to a specific panel in a figure, for instance figure \ref{f:panel1} or figure \ref{f:panel2}. Its also possible to refer to the entire figure, for instance figure \ref{f:graph1} or figure \ref{f:graph2}. It is also possible to refer to a panel within a figure by itself, for instance panel \subref{f:panel1} or panel \subref{f:panel2} in figure \ref{f:graph1}.

@@

\subsection{A full-page graph}
